---
title: "Tamalow Card Game"
output: html_notebook
runtime: shiny
---

This is an R Markdown Notebook that works through the steps to create a digital version of the card game Tamalow.  

The first section of code creates an array that represents a fifty two card deck. 

```{r echo = FALSE, message = FALSE}
library(shiny)
library(DT)

deck <- array(NA,52)
playernames <- list("Jo", "Dave", "Will", "Arkie")
houses <- list("S","D","C","H")
card <- list("A", "2", "3", "4", "5", "6", "7", "8", "9", "10", "J", "Q", "K")

t <- 0
for (i in 1:4){
  for(j in 1:13){
    t <- t+1
    deck[t] <- paste0(card[j],houses[i])
  }
}



```

The next section randomly deals cards between four named players and creates the Tallow object that holds the information for the game. Each players cards form a dataframe then the reveal and deck are also contained and a seperate list of the player names. At this stage we are trying to run plays with full view of cards to track how the game progresses and ensure the correct plays occur when plays are activated.

Eventually this information will be contained in an external database. The database will hold information on the game and the players in the game, the cards, what has been dealt and where the game is upto. The player login will be used as an environmental variable that will be used to restrict access to certain information. The login will allow initial viewing of the two cards for each person on a separate device. It will also restrict access to the player whose turn it is to see and interact.


```{r echo = FALSE}
 
  players <- data.frame("Jo"=1:4,"Dave"=1:4,"Will"=1:4,"Arkie"=1:4)
   
for (p in 1:4){
  randomnum <- floor(runif (1, min = 1, max = length(deck)))
  players$Arkie[p] <- deck[randomnum]
  deck <- deck[-randomnum]
  
  randomnum <- floor(runif (1, min = 1, max = length(deck)))
  players$Dave[p] <- deck[randomnum]
  deck <- deck[-randomnum]
  
  randomnum <- floor(runif (1, min = 1, max = length(deck)))
  players$Will[p] <- deck[randomnum]
  deck <- deck[-randomnum]
  
  randomnum <- floor(runif (1, min = 1, max = length(deck)))
  players$Jo[p] <- deck[randomnum]
  deck <- deck[-randomnum]
}

  randomnum <- floor(runif (1, min = 1, max = length(deck)))
  reveal <- deck[randomnum]
  deck <- deck[-randomnum]
  
  tamallow <- list(players = players, deck = deck, reveal = reveal, playernames = playernames)

 
```



Enable players to select the cards that they want to play

```{r echo = FALSE}
selectInput("option", label = h3("Play Choice"),
            choices = list("Select Card From Deck" = 1, "Select Card From Throwaway Pile" = 2, "Play Rule Card" =  3), 
            multiple = FALSE, selected = NULL)

conditionalPanel(
  condition = "input.option == 1",
  checkboxGroupInput("JocheckGroup", label = h3("Jo's Cards"), 
    choices = list("Card 1" = 1, "Card 2" = 2, "Card 3" = 3, "Card 4" = 4),
    selected = NULL)
)

# observeEvent(input$option,{
#   if(input$option == 1){ 
#     print(10)
#     checkboxGroupInput("JocheckGroup", label = h3("Jo's Cards"), 
#     choices = list("Card 1" = 1, "Card 2" = 2, "Card 3" = 3, "Card 4" = 4),
#     selected = NULL)}else{}
  
  
#} )

# checkboxGroupInput("JocheckGroup", label = h3("Jo's Cards"), 
#     choices = list("Card 1" = 1, "Card 2" = 2, "Card 3" = 3, "Card 4" = 4),
#     selected = NULL)
# 
# checkboxGroupInput("ArkiecheckGroup", label = h3("Arkie's Cards"), 
#     choices = list("Card 1" = 1, "Card 2" = 2, "Card 3" = 3, "Card 4" = 4),
#     selected = NULL)
# 
# checkboxGroupInput("WillcheckGroup", label = h3("Will's Cards"), 
#     choices = list("Card 1" = 1, "Card 2" = 2, "Card 3" = 3, "Card 4" = 4),
#     selected = NULL)
# 
# checkboxGroupInput("DavecheckGroup", label = h3("Dave's Cards"), 
#     choices = list("Card 1" = 1, "Card 2" = 2, "Card 3" = 3, "Card 4" = 4),
#     selected = NULL)
```

Using an "End Turn" button to activate next turn and define whose go is next

```{r echo = FALSE}
players <- list(newplayer=playernames[length(playernames)], nextplayerid=length(playernames))
players$nextplayerid <- 1
players$newplayer <- playernames[as.numeric(players$nextplayerid)]
actionButton("turnend", "End Turn and Play Selection")

nextplayer <- eventReactive(input$turnend, {
  
  #if(input$turnend<1){nextplayerid <- nextplayerid+1}else {nextplayerid <- players$nextplayerid + 1 }
  players$nextplayerid <- players$nextplayerid + 1
  
  if (players$nextplayerid>length(tamallow$playernames)){
    players$nextplayerid <- 1
  }
  
 players$newplayer <- playernames[as.numeric(players$nextplayerid)]
  
  players
})

```



A series of buttons to run the different plays

```{r echo = FALSE}

# actionButton("deal", "Swap")
# 
playerss <- eventReactive(input$turnend, {

  pippy <- length(tamallow$reveal)
  deckcard <- tamallow$reveal[pippy]
  playercard <- tamallow$players$Dave[as.numeric(input$DavecheckGroup)]
  tamallow$reveal[pippy] <- playercard
  tamallow$players$Dave[as.numeric(input$DavecheckGroup)] <- deckcard
  tamallow

})



```

Deck Card and Upturned Card

```{r echo = FALSE}
fluidRow(column (3, renderImage({
  return(list(
        click = "turn",
        width = "150",
        src = "PNG/red_back.png",
        contentType = "image/png",
        alt = "Card"
      ))
 }, deleteFile = FALSE ))
 
)
```


This section creates the viewing output for the player whose turn it is

<font size="11">Name of player whose turn it is:</font>

```{r echo = FALSE}

h3(renderText({
  if (input$turnend == 0){as.character(players$newplayer[[1]])}else{
 players <<- nextplayer()
  chipper <<- as.character(players$newplayer[[1]])

  chipper}
}))
```

<font size="11">Cards:</font>

```{r echo = FALSE}

fluidRow(column (3, renderImage({
  return(list(
        click = "turn",
        width = 150,
        src = "PNG/red_back.png",
        contentType = "image/png",
        alt = "Card"
      ))
 }, deleteFile = FALSE )),

 column(3,
renderImage({
  return(list(
        width = 150,
        src = "PNG/red_back.png",
        contentType = "image/png",
        alt = "Card"
      ))
 }, deleteFile = FALSE )),
column(3,
renderImage({ card3 <- nextplayer()
  return(list(
        width = 150,
        src = paste0("PNG/",tamallow$players[3,card3$nextplayerid], ".png"),
        contentType = "image/png",
        alt = "Card"
      ))
 }, deleteFile = FALSE )), 
column(3,
renderImage({ card4 <- nextplayer()
  return(list(
        width = 150,
        src = paste0("PNG/",tamallow$players[4,card4$nextplayerid], ".png"),
        contentType = "image/png",
        alt = "Card"
      ))
 }, deleteFile = FALSE )) )

renderDataTable({
  
  tamallow$players
   })
 
 renderText({
   
   if(input$turnend==0){
      
     tamallow$reveal} else{tamallow<-playerss()
  tamallow$reveal}
})
 
 
renderText({
 length(tamallow$deck)
})



```


```{r echo = FALSE}



```


Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Cmd+Option+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Cmd+Shift+K* to preview the HTML file). 

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.

